The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-18 article.tex
changed coef table

% for adjusting table width automatically
\usepackage{adjustbox}
\usepackage{tabulary, ragged2e}
\usepackage{booktabs}

@@

The first subset of data (used for Model 1 and Model 2, see Table\ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 separate vineyards.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table\ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards.Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

\begin{table}[]
  \caption{Summary of each Models coefficients for continuous variables}\label{tab:contvar}
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}cllllll@{}}
  \toprule
    & \textbf{Intercept} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ Water\\ Used\end{tabular}}} \\ \midrule
  \textbf{Model 1} & -3.318E-02 & 7.418E-01 & 8.660E-02 & 6.731E-02 &  &  \\
  \textbf{Model 2} & -6.516E-01 & 5.774E-01 & 1.079E-02 & 8.498E-02 & -4.971E-02 & -5.346E-02 \\
  \textbf{Model 3} & 1.808E-02 & 9.713E-01 & -2.310E-02 & -6.992E-03 &  &  \\
  \textbf{Model 4} & 6.702E-01 & -7.354E-01 & -6.732E-03 & -5.645E-03 & 2.726E-02 & 7.515E-02 \\
  \textbf{Model 5} & 1.2008636941 &  & -0.040359875 & -0.017057894 &  &  \\
   \bottomrule
\end{tabular}}
\end{table}

@@

Table \ref{tab:kfold} shows the validation results of each of the models. The $R^2$ measures of fit show similar results to the original models, with a slight decrease. Indicating that the models are robust and consistent.
\par
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
    \end{tabular}
  }
  \end{table}

>>>>

% for adjusting table width automatically
\usepackage{adjustbox}
\usepackage{tabulary, ragged2e}
\usepackage{booktabs}
\usepackage{multirow}

@@

The first subset of data (used for Model 1 and Model 2, see Table \ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 separate vineyards.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table \ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards.Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

\begin{table}[]
  \caption{Summary of each Models coefficients for continuous variables}\label{tab:contvar}
  \resizebox{\textwidth}{!}{
    \begin{tabular}{@{}cccccccc@{}}
      \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{} & \textbf{} & \textbf{Intercept} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ *\\ Scope One Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ * \\ Water Used\end{tabular}} \\ \midrule
        \multirow{2}{*}{Model 1} & Coefficient & -0.0332 & 0.7418 & 0.0866 & 0.0673 &  &  \\
         & Std Error & 0.0196 & 0.0100 & 0.0089 & 0.0080 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 2} & Coefficient & 0.1696 & 0.5774 & 0.1079 & 0.0850 & -0.0497 & -0.0535 \\
         & Std Error & 0.0591 & 0.0148 & 0.0131 & 0.0117 & 0.0081 & 0.0084 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 3} & Coefficient & 0.0181 & 0.9713 & -0.0231 & -0.0070 &  &  \\
         & Std Error & 0.0130 & 0.0072 & 0.0069 & 0.0057 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 4} & Coefficient & 0.1450 & 0.0024 & -0.0466 & -0.0170 & 0.0115 & 0.0014 \\
         & Std Error & 0.0528 & 0.0150 & 0.0143 & 0.0118 & 0.0079 & 0.0083 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 5} & Coefficient & 0.1517 &  & -0.0404 & -0.0171 &  &  \\
         & Std Error & 0.0527 &  & 0.0113 & 0.0097 &  &  \\ \bottomrule
        \end{tabular}

      \end{tabular}      
  }
\end{table}

@@

Table \ref{tab:kfold} shows the validation results of each of the models. The $R^2$ measures of fit show similar results to the initial models, with a slight decrease. Indicating that the models are robust and consistent.
%
%
% At least summary statistics of the baseline model.
%
%
\par
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  % \resizebox{\textwidth}{!}{
  \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
    \end{tabular}
  % }
  \end{table}
